*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-12 Code/Manuscript_O2.Rmd
Removed FinguresIN from O2Anaylsis directory

```{r set project variables, include = FALSE}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "CleanData")
FiguresIn <- file.path("..","Output", "Figures")
FigureInO2Analy <- file.path(  "..", "..", "O2Analyses", "Output")

>>>>

```{r set project variables, include = FALSE}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "CleanData")
FiguresIn <- file.path("..","Output", "Figures")
